\thetitle

### 2022-04-01 paper/paper.tex
paragraph about risk aversion

\begin{example} \label{tightexampleforoneoverhopt}
\ifen
Pick any $h$ and let $m = 2h$. For a small constant $\varepsilon \in (0, 1)$, define the market as follows.
\else
임의의 $h$를 택하고 $m = 2h$라고 하자. 작은 상수  $\varepsilon \in (0, 1)$에 대해 시장을 다음처럼 구성한다.
\fi
\begin{align*}
t &= \Bigl(\,\underbrace{1,  \dots, 1}_{h},\;
\underbrace{\varepsilon^{-1}, \varepsilon^{-2}, \dots, \varepsilon^{-(h-1)}, \varepsilon^{-h}}_{h}\,\Bigr) \\
\text{and}\quad f &= \Bigl(\,\underbrace{1,  \dots, 1}_{h},\;
\underbrace{\varepsilon^{1}, \varepsilon^{2}, \dots, \varepsilon^{h-1}, \varepsilon^{h}}_{h}\,\Bigr)
\end{align*}
\ifen
Since all $f_j t_j = 1$, the na\"ive algorithm can choose $\mathcal{T}_h = \{1, \dots, h\}$, with $v(\mathcal{T}_h) = 1$. But the optimal solution is $\mathcal{X}_h = \{h+1, \dots, m\}$, with
\else
모든 $f_j t_j = 1$이므로 나이브 해법은 $\mathcal{T}_h = \{1, \dots, h\}$를 출력할 수 있으며 $v(\mathcal{T}_h) = 1$이다. 그러나 최적해는 $\mathcal{X}_h = \{h+1, \dots, m\}$이며 그의 기대 효용은 다음과 같다.
\fi
\begin{equation*}
v(\mathcal{X}_h) = \sum_{j= h +1}^m \Bigl( f_j t_j \prod_{j' = j+1}^m (1 - f_{j'}) \Bigr) =  \sum_{j= 1}^h  (1 - \varepsilon)^{j} \approx h\ifen.\fi
\end{equation*}
\ifen
Thus, as $\varepsilon$ approaches zero, we have $v(\mathcal{T}_h) / v(\mathcal{X}_h) \to 1/h$. (The optimality of $\mathcal{X}_h$ follows from the fact that it achieves the upper bound of Theorem \ref{oneoverhopt}.)
\else
따라서 $\varepsilon$이 0에 가까워지면서 $v(\mathcal{T}_h) / v(\mathcal{X}_h) \to 1/h$이 된다.  ($\mathcal{X}_h$의 최적성은 정리 \ref{oneoverhopt}이(가) 제시하는 상한을 실천하기 때문에 성립한다.)
\fi
\end{example}

@@

\begin{proof}\ifen
By induction on $h$. Applying Theorem \ref{assumetzerozero}, we assume that $t_0 = 0$. We also assume that each $f_j < 1$, which is without loss of generality because any school having $f_j = 1$ can be eliminated by setting $t_0 = t_j$ and reapplying the transformation from Theorem \ref{assumetzerozero}.

(Base case.) First, we will show that $\mathcal{X}_1 \subset \mathcal{X}_2$. To get a contradiction, suppose that the optima are $\mathcal{X}_1 = \{j\}$ and $\mathcal{X}_2 = \{k, l\}$, where we may assume that $t_k \leq t_l$. Optimality requires that
\else$h$에 대해 귀납법을 적용한다. 정리 \ref{assumetzerozero}에 따라 $t_0 = 0$이라고 가정한다. 또한 모든 $f_j < 1$임을 가정한다. $f_j = 1$인 학교가 있으면 $t_0 = t_j$로 수정하고  정리 \ref{assumetzerozero}의 변환을 다시 적용해서 소거할 수 있으므로 일반성을 제한하지 않는다.

@@

\ifen Suppose $k \notin \mathcal{X}_h$. To get a contradiction, assume that $v(\mathcal{Y}_h) < v(\mathcal{X}_h)$. Then
\else $k \notin \mathcal{X}_h$인 경우를 고려하자. 모순을 보이기 위해 $v(\mathcal{Y}_h) < v(\mathcal{X}_h)$라고 하면 \fi
\begin{align}
\begin{split}
v(\mathcal{X}_{h+1})&= v(\mathcal{Y}_{h} \cup \{k\}) \\
&= (1 - f_k) v(\mathcal{Y}_h) + f_k t_k \\
& < (1 - f_k) v(\mathcal{X}_h) + f_k \operatorname{E}\bigl[ \max\{t_k, X_h\}\bigr]\\
&=  v(\mathcal{X}_h\cup \{k\})
\end{split}
\end{align}
\ifen contradicts the optimality of $\mathcal{X}_{h+1}$.
\else 이는 $\mathcal{X}_{h+1}$의 최적성을 위반한다.\fi

@@

\ifen 
It is also possible to store $\mathcal{C}$ as a binary max heap rather than a list. The heap is ordered according to the criterion $i \geq j \iff f_i t_i \geq f_j t_j$, and by draining the heap and reheapifying at the end of each iteration, the computation time remains $O(hm)$. However, in our numerical experiments, whose results are reported in Section \ref{numericalexperiments},
we found the list implementation to be much faster, because it is possible to identify the entering school $k$ as the utility parameters are updated, which all but eliminates the cost of the $\argmax\{\}$ operation. 
\else
$\mathcal{C}$는 목록 대신 이진 최대 힙 구현으로 저장하는 방법도 고려한다. 단, 힙의 순서는 $i \geq j \iff f_i t_i \geq f_j t_j$의 조건으로 정의하며, 각 반복단계의 마지막 단계에서 힙을 비우고 다시 힙화(heapify)하면 $O(hm)$ 계산 시간을 유지할 수 있다. 그러나 (\ref{numericalexperiments}절에서 결과를 제시할) 수리 실험에서 목록 구현으로 구성한 알고리즘이 더 빨랐다. 효용 모수를 수정하면서 $k$를 구함으로 $\argmax\{\}$ 연산의 계산 비용을 거의 제거할 수 있기 때문이다.
\fi

@@

\ifen \subsection{A small example} \else \subsection{작은 예} \fi
\ifen 
Let us consider a fictional admissions market consisting of $m=8$ schools. The school data, along with the optimal solutions for each $h \leq m$, appear in Table \ref{planetsdata}.
\else 
$m = 8$개의 학교로 구성된 가상 입학 시장을 고려하자. 학교 자료와 각 $h \leq m$에 대응하는 최적해는 표 \ref{planetsdata}에서 나타난다.
\fi

@@

\ifen 
An intuitive extension of the greedy algorithm for Alma's problem is to iteratively add to $\mathcal{X}$ the school $k$ for which $[ v(\mathcal{X}\cup\{k\}) - v(\mathcal{X}) ] / g_k$ is largest. However, the construction above shows that the objective function of Ellis's problem can approximate that of a knapsack problem with arbitrary precision. Therefore, in pathological examples such as the following, the greedy algorithm can achieve an arbitrarily small approximation ratio. 
\else
알마 문제를 위한 탐욕 해법의 직관적인 확장은 $[ v(\mathcal{X}\cup\{k\}) - v(\mathcal{X}) ] / g_k$-값이 가장 높은 학교 $k$를  $\mathcal{X}$에 차례대로 추가하는 것이다. 그러나 위에서 도출한 변환은 엘리스 문제의 목적함수를 배낭 문제의 목적함수의 원하는 만큼 정확한 근사로 만들 수 있음을 의미한다. 따라서 다음 같은 병례에서 탐욕 해법은 임의로 낮은 근사 비율을 일으킬 수 있다.
\fi
\begin{example}
\ifen
Let $t = (10, 2021)$, $f = (1, 1)$, $g = (1, 500)$, and $H = 500$. Then the greedy approximation algorithm produces the clearly inoptimal solution $\mathcal{X} = \{1\}$. 
\else
 $t = (10, 2021)$, $f = (1, 1)$, $g = (1, 500)$, 그리고 $H = 500$이라고 하자. 그러면 탐욕 해법은 $\mathcal{X} = \{1\}$을 출력하며 이는 분명히 최적해가 아니다.
\fi
\end{example} 
% as the following example suggests ...The construction above shows that the objective function of Ellis's problem can approximate that of a knapsack problem with arbitrary precision, and this algorithm

@@

\ifen \subsection{Explicit treatment of risk aversion}\else \subsection{위험 회피가 명시적인 모형}\fi
\ifen
The familiar Markowitz portfolio optimization model includes an explicit risk-aversion term, whereas our model has settled for an implicit treatment of risk, namely the tradeoff between selective schools and safety schools inherent in the maximax objective function. However, it is possible to augment the objective function $v(\mathcal{X}) = \operatorname{E}[X]$ to incorporate a variance penalty $\beta \geq 0$ as follows:
\else
익숙한 Markowitz 포트폴리오 최적화 모형에는 명시적인 위험 회피 항이 있으며, 본 모형은 maximax 목적함수에 내포된 경쟁적인 학교와 안정 학교 사이의 균형에 의한 위험 관리 요소만 고려했다. 그러나 기본 목적함수인 $v(\mathcal{X}) = \operatorname{E}[X]$에 평균편차 페널티 $\beta \geq 0$를 다음처럼 도입할 수 있다:
\fi
\begin{align}
\begin{split}
v_{\mathrm{\beta}}(\mathcal{X}) &=  \operatorname{E}[X] - \beta \operatorname{Var}(X) \\
&=   \operatorname{E}[X] - \beta \left(  \operatorname{E}[X^2]  -  \operatorname{E}[X]^2 \right) \\
& = \sum_{j\in\{0\}\cup\mathcal{X}} \Bigl( f_j t_j \prod_{\substack{i \in \mathcal{X}: \\ i > j}} (1 - f_{i}) \Bigr)
 - \beta \sum_{j\in\{0\}\cup\mathcal{X}} \Bigl( f_j t_j^2 \prod_{\substack{i \in \mathcal{X}: \\ i > j}} (1 - f_{i}) \Bigr)
  + \beta v(\mathcal{X})^2 \\
  &= v(\mathcal{X}; \tau) +  \beta v(\mathcal{X}; t)^2
\end{split}
\end{align}
\ifen
where $\tau_j = t_j - \beta t_j^2$. Since the first term is itself a portfolio valuation function, and the second is a monotonic transformation of one, we speculate that one of the algorithms given above could be used as a subroutine to trace out the efficient frontier by maximizing $v(\mathcal{X}; t)$ subject to the budget constraint and $v(\mathcal{X}; \tau) \geq \alpha$ for various values of $\alpha \geq 0$. 
\else
단, $\tau_j = t_j - \beta t_j^2$. 이의 첫번째 항 그 자체가 포트폴리오 가치 함수이며, 두번째 항은 포트폴리오 가치 함수의 단조 변환이다. 따라서 위에서 제시한 알고리즘을 서브루틴으로 사용하면 효율적 투자선(efficient frontier)을 탐색할 수 있어 보인다. 이때 다양한 $\alpha \geq 0$에 대해 예산 제약식과 $v(\mathcal{X}; \tau) \geq \alpha$ 하에서 $v(\mathcal{X}; t)$을 최대화하는 것이 알고리즘의 요점이다.
\fi

\ifen \subsection{Signaling strategies}\else \subsection{시그런 전략}\fi
\ifen
Another direction of further research with immediate application in college admissions is to incorporate additional signaling strategies into the problem. In the Korean admissions process, the online application form contains three multiple-choice fields, labeled \emph{ga, na,} and \emph{da} for the first three letters of the Korean alphabet, which students use to indicate the colleges to which they wish to apply. Most schools appear only in one or two of the three fields. Therefore, students are restricted not only in the number of applications they can submit, but in the combinations of schools that may coincide in a feasible application portfolio. From a portfolio optimization perspective, this is a \emph{diversification constraint,} because its primary purpose is to prevent students from applying only to top-tier schools. However, in addition to overall selectivity, the three fields also indicate different evaluation schemes: Applications filed under the \emph{ga} and {na} fields are evaluated with greater emphasis on standardized-test scores than those filed under the \emph{da} field. Some colleges appear in multiple fields and run two parallel admissions processes, each with different evaluation criteria. Therefore, if a student recognizes that she has a comparative advantage in (for example) her interview skills, she may increase her chances of admission to a competitive school by applying under the \emph{ga} field. Clearly, the optimal application strategy in this context can be quite subtle, and are a perennial subject of debate on Korean social networks.

An analogous feature of the American college admissions process is known as early decision, in which at the moment of application, a student commits to enrolling in a college if admitted. In principle, students who apply with early decision may obtain a better chance of admission by signaling their eagerness to attend, but doing so weakens the college's incentive to entice the student with merit-based financial aid, altering the utility calculus.
\else
향후 연구에 두번째 방향은 모형에 시그널 전략을 도입하는 것이다. 한국 입학 과정의 온라인 지원 양식에는 가군, 나군, 다군이란 3가지 선다형 칸을 채워서 지원하는 학교를 선택한다. 대부분의 학교는 모든 3개의 칸에 등장하지 않고 그 중 1~2개만 가능하다. 따라서 학생이 지원할 수 있는 학교의 `수'일 뿐만 아니라 가능한 지원 포트폴리오에 같이 들어갈 수 있는 학교의 `조합'도 제한된다. 이는 학생이 상위권 대학만 지원하지 않도록 만들어지기 때문에  다각화(diversification) 제약식으로 볼 수 있다. 그러나 대학이 어떤 군에 속하는 것은 대학 순위일 뿐더러 입학 전형 유형도 의미한다. 가군과 나군으로 지원하는 경우, 다군보다 수능 점수의 반영 비율이 높다. 또한 군 2개에 포함되는 학교도 있으며 입학 전형이 다르면서 평행한 모집 과정 2개를 운영한다. 가령, 어떤 학생이 면접 능력에 비교 우위가 있으면 경쟁적인 학교에 가군으로 지원하면 합격 확률을 높일 수 있다. 이런 맥락에서 최적의 지원 전략은 미묘한 문제이며 한국 SNS에서 자주 발생하는 화젯거리다.

미국 입학 과정의 유사한 특징은 조기 전형(early decision)이다. 이는 학생이 합격하면 진학한다고 약속하고 지원하는 것을 의미한다. 조기 전형으로 지원하면 입학할 관심을 시그널할 수 있으므로 합격 확률을 높일 수 있는 반면에, 학교가 학생을 모집하려고 장학금을 수여할 동기가 약화할 수 있으므로 학생의 효용 추정이 달라진다.
\fi

\ifen
In the integer formulation of the college application problem (Problem \ref{integernlp}), a natural way to model these signaling strategies without introducing too much complexity is to split each $c_j$ into $c_{j+}$ and $c_{j-}$. The binary decision variables are $x_{j+} = 1$ if the student applies to $c_j$ with high priority (that is, in  the \emph{ga} or \emph{na} field or with early decision) and $x_{j-} = 1$ if applying with low priority (that is, in the \emph{da} field or without early decision). Now, assuming that the differential admission probabilities $f_{j+}$ and $f_{j-}$ and utilities $t_{j+}$ and $t_{j-}$ are known, adding the logical constraints 
\begin{align}
 x_{j+} + x_{j-} \leq 1, ~~ j = 1\dots m\qquad\text{and}\qquad\sum_{j=1}^m x_{j+} \leq 1
\end{align}
completes the formulation. These constraints are conformable to those of the multiple knapsack problem (Kellerer et al. 2004, chap. 10). 
\else
대학 지원 문제의 정수 모형(문제 \ref{integernlp})에서 위의 시그널 전략들을 어렵지 않게 도입하는 방식은 각 $c_j$를 $c_{j+}$와 $c_{j-}$로 나누는 것이다. 그다음에 학생이 $c_j$에 높은 관심을 시그널하면 (즉, 가군으로 선택하거나 조기 전형으로 지원하면) $x_{j+} = 1$이며 관심을 시그널 하지 않고 지원하면 (즉 가군 혹은 나군으로 지원하거나 조기 전형 없이 지원하면) $x_{j-} = 1$이 되는 이진 결정 변수를 정의한다. 그러면 해당 합격 확률 $f_{j+}$와 $f_{j-}$ 그리고 효용  $t_{j+}$와 $t_{j-}$가 알려져 있다고 가정하면 다음 같은 논리 제약식을 더해서 모형을 완성할 수 있다. 
\begin{align}
 x_{j+} + x_{j-} \leq 1, ~~ j = 1\dots m\qquad\text{그리고}\qquad\sum_{j=1}^m x_{j+} \leq 1
\end{align}
다중 배낭 문제의 제약식과 같을 꼴이다 (Kellerer et al. 2004, 10제). 
\fi

@@

추상적인 관점에서, 알고리즘 \ref{ellisDP1}과(와) 알고리즘 \ref{ellisDP3}은(는) 최적해를 $Z[N, C]$로 표현하는 2차원 동적 계획이다. 이때 $N$은 결정 변수의 수, $C$는 제약식의 모수, 그리고 $Z[n, c]$는 제약 모수가 $c \leq C$일 때 첫 $n\leq N$개의 결정 변수만 이용하는 최적해이다. 알고리즘의 구조는 $Z[n, c]$를 $Z[n -1, c]$와 어떤 $c' \leq c$에 대응하는 $Z[n -1, c']$의 함수로 표현하는 반복 관계로 탐색하는 것이다. (알고리즘 \ref{ellisDP1}에서 $Z$는 최대 포트폴리오 가치, $N = m$, 그리고 $C =H$이며, 알고리즘 \ref{ellisDP3}에서 $Z$는 최소한 지원 지출액, $N = m$, 그리고 $C= |\mathcal{V}| \propto m^2 / \varepsilon$이다.)

>>>>

\begin{example} \label{tightexampleforoneoverhopt}
\ifen
Pick any $h$ and let $m = 2h$. For a small constant $\varepsilon \in (0, 1)$, define the market as follows.
\else
임의의 $h$를 택하고 $m = 2h$라고 하자. 작은 상수  $\varepsilon \in (0, 1)$에 대해 시장을 다음처럼 구성한다.
\fi
\begin{align*}
 f &= \Bigl(\,\underbrace{1,  \dots, 1}_{h},\;
\underbrace{\varepsilon^{1}, \varepsilon^{2}, \dots, \varepsilon^{h-1}, \varepsilon^{h}}_{h}\,\Bigr) \\
\text{\ifen and\else 그리고\fi}\quad t &= \Bigl(\,\underbrace{1,  \dots, 1}_{h},\;
\underbrace{\varepsilon^{-1}, \varepsilon^{-2}, \dots, \varepsilon^{-(h-1)}, \varepsilon^{-h}}_{h}\,\Bigr) 
\end{align*}
\ifen
Since all $f_j t_j = 1$, the na\"ive algorithm can choose $\mathcal{T}_h = \{1, \dots, h\}$, with $v(\mathcal{T}_h) = 1$. But the optimal solution is $\mathcal{X}_h = \{h+1, \dots, m\}$, with
\else
모든 $f_j t_j = 1$이므로 나이브 해법은 $\mathcal{T}_h = \{1, \dots, h\}$를 출력할 수 있으며 $v(\mathcal{T}_h) = 1$이다. 그러나 최적해는 $\mathcal{X}_h = \{h+1, \dots, m\}$이며 그의 기대 효용은 다음과 같다.
\fi
\begin{equation*}
v(\mathcal{X}_h) = \sum_{j= h +1}^m \Bigl( f_j t_j \prod_{j' = j+1}^m (1 - f_{j'}) \Bigr) =  \sum_{j= 1}^h  (1 - \varepsilon)^{j} \approx h\ifen.\fi
\end{equation*}
\ifen
Thus, as $\varepsilon$ approaches zero, we have $v(\mathcal{T}_h) / v(\mathcal{X}_h) \to 1/h$. (The optimality of $\mathcal{X}_h$ follows from the fact that it achieves the upper bound of Theorem \ref{oneoverhopt}.)
\else
따라서 $\varepsilon$이 0에 가까워지면서 $v(\mathcal{T}_h) / v(\mathcal{X}_h) \to 1/h$이 된다.  ($\mathcal{X}_h$의 최적성은 정리 \ref{oneoverhopt}이(가) 제시하는 상한을 실천하기 때문에 성립한다.)
\fi
\end{example}

@@

\begin{proof}\ifen
By induction on $h$. Applying Theorem \ref{assumetzerozero}, we assume that $t_0 = 0$.

(Base case.) First, we will show that $\mathcal{X}_1 \subset \mathcal{X}_2$. To get a contradiction, suppose that the optima are $\mathcal{X}_1 = \{j\}$ and $\mathcal{X}_2 = \{k, l\}$, where we may assume that $t_k \leq t_l$. Optimality requires that
\else$h$에 대해 귀납법을 적용한다. 정리 \ref{assumetzerozero}에 따라 $t_0 = 0$이라고 가정한다.

@@

\ifen Suppose $k \notin \mathcal{X}_h$. To get a contradiction, suppose that $v(\mathcal{Y}_h) < v(\mathcal{X}_h)$ and  $v(\mathcal{X}_{h+1}) > v(\mathcal{X}_h \cup \{k\})$. Then
\else $k \notin \mathcal{X}_h$인 경우를 고려하자. 모순을 보이기 위해 $v(\mathcal{Y}_h) < v(\mathcal{X}_h)$ 그리고 $v(\mathcal{X}_{h+1}) > v(\mathcal{X}_h \cup \{k\})$라고 가정하면 다음이 성립한다. \fi
\begin{align}
\begin{split}
v(\mathcal{X}_{h+1})&= v(\mathcal{Y}_{h} \cup \{k\}) \\
&= (1 - f_k) v(\mathcal{Y}_h) + f_k t_k \\
&\leq (1 - f_k) v(\mathcal{X}_h) + f_k \operatorname{E}\bigl[ \max\{t_k, X_h\}\bigr]\\
&=  v(\mathcal{X}_h\cup \{k\})
\end{split}
\end{align}
\ifen is a contradiction.
\else 모순이다.\fi

@@

\ifen 
It is possible to store $\mathcal{C}$ as a binary max heap rather than a list. The heap is ordered according to the criterion $i \geq j \iff f_i t_i \geq f_j t_j$, and by draining the heap and reheapifying at the end of each iteration, the computation time remains $O(hm)$. However, in our numerical experiments, whose results are reported in Section \ref{numericalexperiments},
we found the list implementation to be much faster, because it is possible to identify the entering school $k$ as the utility parameters are updated, which all but eliminates the cost of the $\argmax\{\}$ operation. 
\else
$\mathcal{C}$는 목록 대신 이진 최대 힙 구현으로 저장하는 방법도 고려한다. 단, 힙의 순서는 $i \geq j \iff f_i t_i \geq f_j t_j$의 조건으로 정의하며, 각 반복단계의 마지막 단계에서 힙을 비우고 다시 힙화(heapify)하면 $O(hm)$ 계산 시간을 유지할 수 있다. 그러나 (\ref{numericalexperiments}절에서 결과를 제시할) 수리 실험에서 목록 구현으로 구성한 알고리즘이 더 빨랐다. 효용 모수를 수정하면서 $k$를 구함으로 $\argmax\{\}$ 연산의 계산 비용을 거의 제거할 수 있기 때문이다.
\fi

@@

\ifen \subsection{A small example} \else \subsection{작은 예} \fi \label{planetsexamplesection}
\ifen 
Let us consider a fictional admissions market consisting of $m=8$ schools. The school data, along with the optimal solutions for each $h \leq m$, appear in Table \ref{planetsdata}.
\else 
$m = 8$개의 학교로 구성된 가상 입학 시장을 고려하자. 학교 자료와 각 $h \leq m$에 대응하는 최적해는 표 \ref{planetsdata}에서 나타난다.
\fi

@@

\ifen 
An intuitive extension of the greedy algorithm for Alma's problem is to iteratively add to $\mathcal{X}$ the school $k$ for which $\bigl( v(\mathcal{X}\cup\{k\}) - v(\mathcal{X}) \bigr) / g_k$ is largest. However, the construction above shows that the objective function of Ellis's problem can approximate that of a knapsack problem with arbitrary precision. Therefore, in pathological examples such as the following, the greedy algorithm can achieve an arbitrarily small approximation ratio. 
\else
알마 문제를 위한 탐욕 해법의 직관적인 확장은 $\bigl( v(\mathcal{X}\cup\{k\}) - v(\mathcal{X}) \bigr) / g_k$-값이 가장 높은 학교 $k$를  $\mathcal{X}$에 차례대로 추가하는 것이다. 그러나 위에서 도출한 변환은 엘리스 문제의 목적함수를 배낭 문제의 목적함수의 원하는 만큼 정확한 근사로 만들 수 있음을 의미한다. 따라서 다음 같은 병례에서 탐욕 해법은 임의로 낮은 근사 비율을 일으킬 수 있다.
\fi
\begin{example}
\ifen
Let $t = (10, 2021)$, $f = (1, 1)$, $g = (1, 500)$, and $H = 500$. Then the greedy approximation algorithm produces the clearly inoptimal solution $\mathcal{X} = \{1\}$. 
\else
 $t = (10, 2021)$, $f = (1, 1)$, $g = (1, 500)$, 그리고 $H = 500$이라고 하자. 그러면 탐욕 해법은 $\mathcal{X} = \{1\}$을 출력하며 이는 분명히 최적해가 아니다.
\fi
\end{example} 
% as the following example suggests ...The construction above shows that the objective function of Ellis's problem can approximate that of a knapsack problem with arbitrary precision, and this algorithm

@@

\ifen \subsection{Explicit treatment of risk aversion}\else \subsection{위험 회피가 명시적인 모형}\fi
\ifen
The familiar Markowitz portfolio optimization model includes an explicit risk-aversion term, whereas our model has settled for an implicit treatment of risk, namely the tradeoff between selective schools and safety schools inherent in the maximax objective function. However, it is possible to augment the objective function $v(\mathcal{X}) = \operatorname{E}[X]$ to incorporate a variance penalty $\beta \geq 0$ as follows:
\else
익숙한 Markowitz 포트폴리오 최적화 모형에는 명시적인 위험 회피 항이 등장하며, 본 모형은 maximax 목적함수에 내포된 경쟁적인 학교와 안정 지원 학교 사이의 균형에 의한 위험 관리 요소만 고려했다. 그러나 기본 목적함수인 $v(\mathcal{X}) = \operatorname{E}[X]$에 평균편차 페널티 $\beta \geq 0$를 다음처럼 도입할 수 있다:
\fi
\begin{align}
\begin{split}
v_{\mathrm{\beta}}(\mathcal{X}) &=  \operatorname{E}[X] - \beta \operatorname{Var}(X) \\
&=   \operatorname{E}[X] - \beta \left(  \operatorname{E}[X^2]  -  \operatorname{E}[X]^2 \right) \\
& = \sum_{j\in\{0\}\cup\mathcal{X}} \Bigl( f_j t_j \prod_{\substack{i \in \mathcal{X}: \\ i > j}} (1 - f_{i}) \Bigr)
 - \beta \sum_{j\in\{0\}\cup\mathcal{X}} \Bigl( f_j t_j^2 \prod_{\substack{i \in \mathcal{X}: \\ i > j}} (1 - f_{i}) \Bigr)
  + \beta v(\mathcal{X})^2 \\
  &= v(\mathcal{X}; \tau) +  \beta v(\mathcal{X}; t)^2
\end{split}
\end{align}
\ifen
where $\tau_j = t_j - \beta t_j^2$. Since the first term is itself a portfolio valuation function, and the second is a monotonic transformation of one, we speculate that one of the algorithms given above could be used as a subroutine to trace out the efficient frontier by maximizing $v(\mathcal{X}; t)$ subject to the budget constraint and $v(\mathcal{X}; \tau) \geq \alpha$ for various values of $\alpha \geq 0$. 
\else
단, $\tau_j = t_j - \beta t_j^2$. 이의 첫번째 항 그 자체가 포트폴리오 가치 함수이며, 두번째 항은 포트폴리오 가치 함수의 단조 변환이다. 따라서 위에서 제시한 알고리즘을 서브루틴으로 사용하면 효율적 투자선(efficient frontier)을 탐색할 수 있어 보인다. 이때 다양한 $\alpha \geq 0$에 대해 예산 제약식과 $v(\mathcal{X}; \tau) \geq \alpha$ 하에서 $v(\mathcal{X}; t)$을 최대화하는 것이 알고리즘의 요점이다.
\fi

A parametric treatment of risk aversion may align our model more closely to real-world applicant behavior. Conventional wisdom asserts that the best college application strategy combines reach, target, and safety schools in roughly equal proportion (Kim 2015). When the application budget is small relative to the size of the admissions market, our algorithms recommend a similar approach (see the example of Section \ref{planetsexamplesection}). However, inspecting equation \eqref{howtotransformfj}, which discounts school utility parameters to reflect their marginal value relative to the schools already in the portfolio, reveals that low-utility schools are penalized more harshly than high utility schools in the marginal analysis. Consequentially, as the application budget grows, the optimal portfolio in our model tends to favor reach schools over safety schools. (See Figure \ref{samplemarket} for a clear illustration of this phenomenon.)

A potential application of our model is an econometric study that estimates students’ perceptions of college quality ($t_j$) from their observed application behavior ($\mathcal{X}$) under the assumption of utility maximization. However, empirical research indicates that risk aversion is a significant factor in human decision-making, including in the domains of educational choice and employment search (Kahneman 2011; Hartlaub and Schneider 2012; van Huizen and Alessie 2019). Therefore, an endogenous risk-aversion parameter would greatly enhance our model’s explanatory power in the econometric setting.

\ifen \subsection{Signaling strategies}\else \subsection{시그런 전략}\fi
\ifen
Another direction of further research with immediate application in college admissions is to incorporate additional signaling strategies into the problem. In the Korean admissions process, the online application form contains three multiple-choice fields, labeled \emph{ga, na,} and \emph{da} for the first three letters of the Korean alphabet, which students use to indicate the colleges to which they wish to apply. Most schools appear only in one or two of the three fields. Therefore, students are restricted not only in the number of applications they can submit, but in the combinations of schools that may coincide in a feasible application portfolio. From a portfolio optimization perspective, this is a \emph{diversification constraint,} because its primary purpose is to prevent students from applying only to top-tier schools. However, in addition to overall selectivity, the three fields also indicate different evaluation schemes: Applications filed under the \emph{ga} and {na} fields are evaluated with greater emphasis on standardized-test scores than those filed under the \emph{da} field. Some colleges appear in multiple fields and run two parallel admissions processes, each with different evaluation criteria. Therefore, if a student recognizes that she has a comparative advantage in (for example) her interview skills, she may increase her chances of admission to a competitive school by applying under the \emph{ga} field. Clearly, the optimal application strategy in this context can be quite subtle, and it is a subject of perennial debate on Korean social networks.

An analogous feature of the American college admissions process is known as early decision, in which at the moment of application, a student commits to enrolling in a college if admitted. In principle, students who apply with early decision may obtain a better chance of admission by signaling their eagerness to attend, but doing so weakens the college's incentive to entice the student with merit-based financial aid, altering the utility calculus.
\else
향후 연구에 두번째 방향은 모형에 시그널 전략을 도입하는 것이다. 한국 입학 과정의 온라인 지원 양식에는 가군, 나군, 다군이란 3가지 선다형 칸을 채워서 지원하는 학교를 선택한다. 대부분의 학교는 모든 3개의 칸에 등장하지 않고 그 중 1~2개만 가능하다. 따라서 학생이 지원할 수 있는 학교의 `수'일 뿐만 아니라 가능한 지원 포트폴리오에 같이 들어갈 수 있는 학교의 `조합'도 제한된다. 이는 학생이 상위권 대학만 지원하지 않도록 만들어지기 때문에  다각화(diversification) 제약식으로 볼 수 있다. 그러나 대학이 어떤 군에 속하는 것은 대학 순위일 뿐더러 입학 전형 유형도 의미한다. 가군과 나군으로 지원하는 경우, 다군보다 수능 점수의 반영 비율이 높다. 또한 군 2개에 포함되는 학교도 있으며 입학 전형이 다르면서 평행한 모집 과정 2개를 운영한다. 가령, 어떤 학생이 면접 능력에 비교 우위가 있으면 경쟁적인 학교에 가군으로 지원하면 합격 확률을 높일 수 있다. 이런 맥락에서 최적의 지원 전략은 미묘한 문제이며 한국 SNS에서 자주 발생하는 화젯거리이다.

미국 입학 과정의 유사한 특징은 조기 전형(early decision)이다. 이는 학생이 합격하면 진학한다고 약속하고 지원하는 것을 의미한다. 조기 전형으로 지원하면 입학할 관심을 시그널할 수 있으므로 합격 확률을 높일 수 있지만, 학교가 학생을 모집하려고 장학금을 수여할 동기가 약화할 수 있으므로 학생의 효용 추정이 달라진다.
\fi

\ifen
In the integer formulation of the college application problem (Problem \ref{integernlp}), a natural way to model these signaling strategies without introducing too much complexity is to split each $c_j$ into $c_{j+}$ and $c_{j-}$. The binary decision variables are $x_{j+} = 1$ if the student applies to $c_j$ with high priority (that is, in  the \emph{ga} or \emph{na} field or with early decision) and $x_{j-} = 1$ if applying with low priority (that is, in the \emph{da} field or without early decision). Now, assuming that the differential admission probabilities $f_{j+}$ and $f_{j-}$ and utilities $t_{j+}$ and $t_{j-}$ are known, adding the logical constraints 
\begin{align}
 x_{j+} + x_{j-} \leq 1, ~~ j = 1\dots m\qquad\text{and}\qquad\sum_{j=1}^m x_{j+} \leq 1
\end{align}
completes the formulation. These constraints are conformable to those of the multiple knapsack problem (Kellerer et al. 2004, chap. 10). 
\else
대학 지원 문제의 정수 모형(문제 \ref{integernlp})에서 위의 시그널 전략들을 어렵지 않게 도입하는 방식은 각 $c_j$를 $c_{j+}$와 $c_{j-}$로 나누는 것이다. 그다음에 학생이 $c_j$에 높은 관심을 시그널하면 (즉, 가군으로 선택하거나 조기 전형으로 지원하면) $x_{j+} = 1$이며 관심을 시그널 하지 않고 지원하면 (즉 가군 혹은 나군으로 지원하거나 조기 전형 없이 지원하면) $x_{j-} = 1$이 되는 이진 결정 변수를 정의한다. 그러면 해당 합격 확률 $f_{j+}$와 $f_{j-}$ 그리고 효용  $t_{j+}$와 $t_{j-}$가 알려져 있다고 가정하면 다음 같은 논리 제약식을 더하면 모형을 완성할 수 있다. 
\begin{align}
 x_{j+} + x_{j-} \leq 1, ~~ j = 1\dots m\qquad\text{그리고}\qquad\sum_{j=1}^m x_{j+} \leq 1
\end{align}
다중 배낭 문제의 제약식과 같을 꼴이다 (Kellerer et al. 2004, 10제). 
\fi

@@

추상적인 관점에서, 알고리즘 \ref{ellisDP1}과(와) 알고리즘 \ref{ellisDP3}은(는) 최적해를 $Z[N, C]$로 표현하는 2차원 동적 계획이다. 이때 $N$은 결정 변수의 수, $C$는 제약식의 모수, 그리고 $Z[n, c]$는 제약 모수가 $c \leq C$일 때 첫 $n\leq N$개의 결정 변수만 이용하는 최적 목적함수값이다. 알고리즘의 구조는 $Z[n, c]$를 $Z[n -1, c]$와 어떤 $c' \leq c$에 대응하는 $Z[n -1, c']$의 함수로 표현하는 반복 관계로 탐색하는 것이다. (알고리즘 \ref{ellisDP1}에서 $Z$는 최대 포트폴리오 가치, $N = m$, 그리고 $C =H$이며, 알고리즘 \ref{ellisDP3}에서 $Z$는 최소한 지원 지출액, $N = m$, 그리고 $C= |\mathcal{V}| \propto m^2 / \varepsilon$이다.)

이러한 형태의 동적 계획을 표 혹은 사전 기록으로 구현하면 최적해를 출력하는 것은 $O(NC)$-시간과 -공간을 소요한다. Kellerer외 (2004, \S\,3.3)는 동적 계획 $Z$를 $O(N C)$-시간과 $O(N + C)$-공간 안에 최적해를 구하는 분할 정복(divide and conquer) 알고리즘으로 변환하는 일잔적인 방법을 제시하며 매우 유익하다. 그러나 이를 이용할 수 있는 조건 중, 목적함수는 어떤 기술적인 의미에서 가산적으로 분할되어야 하며 이를 대학 지원 문제에 적용하기 어렵다.
\fi
